Kyoto VR MQP Paper First Draft

### 2019-09-25 paper.tex
add more to deploying editour section

While this worked well enough for testing, it was not a permanent solution. We
asked Atticus to provide a more powerful---and geographically closer---hosting
solution for running the Editour in the future. He obtained a domain name and
shared hosting environment for us to use on September 23\textsuperscript{rd}.
Unfortunately, this shared hosting environment was designed for running simple
PHP applications like WordPress, so it took a bit of work to coerce it into
running a Node.js application.

>>>>

While this worked well enough for testing, it was not a permanent solution. We
asked Atticus to provide a more powerful---and geographically closer---hosting
solution for running the Editour in the future. He obtained a domain name and
shared hosting environment on a Red Hat Enterprise Linux (RHEL) server for us to
use on September 23\textsuperscript{rd}. Unfortunately, this shared hosting
environment was designed for running simple PHP applications like WordPress, so
it took a bit of work to coerce it into running a Node.js application.

We were able to get shell access to the shared hosting environment, but without
superuser privileges. This meant we couldn't install packages, change system
settings, or access systemctl. In order to install Node.js and npm in this
environment we had to use Node Version Manager, a series of shell scripts that
handles downloading and compiling various versions of Node~\autocite{nvmsh2019}.
The only difficulty with this was finding a version of Node.js that could
compile with the older version of GCC the RHEL server had. Fortunately the
server already had git installed, so we were able to simply clone the backend
from GitHub and run it with npm.

However, the server already had Apache listening on port 80, and without
superuser privileges we could not edit the Apache configuration files to change
this. Instead we decided to configure Apache as a reverse proxy, using only the
rules that can be put in a \texttt{.htaccess} file, since this is the only
configuration file we could access. Using Apache's \texttt{mod\_rewrite} module
we were able to rewrite incoming requests on port 80 to instead go to
\texttt{localhost:3000}, the port Node.js was listening
on~\autocite{apache2019}.
